Example Manuscript Template for a Data Analysis Project

### 2021-10-08 products/manuscript/Manuscript.Rmd
added data, added to manuscript.rmd, created analysiscode.rmd, generated results (figures and tables)

# Summary/Abstract
I plan to investigate the transmission dynamics of SARS-CoV-2 within Houston and between Houston and surrounding areas (the rest of Texas and the United States).

@@

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_

## Description of data and data source
As of 10/3/2021, there are 88,776 sequences from Texas uploaded to GISAID (beginning in Feb 2020). After downloading these data, I will align sequences to a reference genome via MAFFT and trim them in Geneious. I will subsample these down to ~400 samples, so that the size is workable in BEAST. Since my focus is on Houston, I will randomly subsample these data while keeping 30% of sequences to Houston.

I will also use case incidence data from the Texas Health Department, as of 10/3/2021.

## Questions/Hypotheses to be addressed
Using case incidence data, assess spatial heterogeneity (county-level) of SARS-CoV-2 in Texas.

Using genomic data, phylogeographic analysis (county-level).

# Methods and Results
Discrete trait analysis (county) in BEAST to estimate transition rates between counties, identify statistically supported transitions (BF values), and calculate R0.

@@

Figure \@ref(fig:resultfigure) shows a scatterplot figure produced by one of the R scripts.

```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/resultfigure.png")
```

>>>>

# Summary/Abstract

@@

## General Background Information

## Description of data and data source
Data from the Texas Health Department, as of 10/3/2021.
-New confirmed cases and fatalities by date (n = 579)
-Confirmed cases and fatalities aggregated by county (n = 254)

Download lineage/clade metadata from GISAID for each county

## Questions/Hypotheses to be addressed
Look at spatial heterogeneity within Texas counties (case incidence and mortality)

Estimate the reproductive number for each county

Assess the association between population size, population density, and dominant lineage/clade with case incidence, mortality, and reproductive number (regression model)

Use DSAIDE package, regression methods

# Methods and Results

@@

Figure \@ref(fig:epicurve) shows an epi curve produced by one of the R scripts.

```{r epicurve,  fig.cap='Epi Curve.', echo=FALSE}
knitr::include_graphics("../../results/epicurve.png")
```
